### 2016-09-29 rebuttal.tex

\begin{document}

\includepdf{coverletter.pdf}

\section{Comments from Editor}

\begin{questions}
\question I found the \url{http://live.sympy.org/} site very convenient for trying things
out in SymPy, but it is only mentioned in the supplement, which might be
overlooked by readers. I suggest moving that section into the main paper, as
it provides a great way to play along with the examples while reading the
paper.
\begin{solution}
\label{editorpoint1}
Section (previously) 9 from the supplement was edited and moved to the introduction:
\begin{quote}
  All the examples in this paper can be tested on
  \href{http://live.sympy.org}{SymPy Live}, an online Python shell that uses
  the Google App Engine to execute SymPy code. SymPy Live is also integrated
  in the SymPy documentation at
  \href{http://docs.sympy.org}{http://docs.sympy.org}.
\end{quote}
\end{solution}
\question The Basic Usage section omits what I think is an important point:
how does one distinguish between evaluating exp(1) in Python and exp(1) in
SymPy? In other words, how are symbolic constants specified?
\begin{solution}
  Both Python standard library and SymPy have exp callable, so it depends
  which symbols are imported in your global namespace: the \texttt{exp}
  function from the \texttt{math} module or the \texttt{exp} class from SymPy.
  In the later case a special symbolic constant will be produced.

### 2016-09-29 introduction.tex
Modify SymPy Live paragraph

All examples could be tested on the \href{http://live.sympy.org}{SymPy Live}
instance, that is an online Python shell, which uses the Google App Engine to
execute SymPy code.  The SymPy Live is integrated in the SymPy documentation
system at \href{http://docs.sympy.org}{http://docs.sympy.org}.

>>>>

All the examples in this paper can be tested on
\href{http://live.sympy.org}{SymPy Live}, an online Python shell that uses the
Google App Engine~\cite{ciurana2009google} to execute SymPy code. SymPy Live
is also integrated in the SymPy documentation at
\href{http://docs.sympy.org}{http://docs.sympy.org}.
